Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-26 article/draft.tex
link about misinfo YT added to the summary table in Appendix

                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}  \\ \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}    \end{tabular}                            \\ \hline

>>>>

                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}  \\ \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/} \\ \href{https://blog.youtube/inside-youtube/tackling-misinfo}{https://blog.youtube/inside-youtube/tackling-misinfo}    \end{tabular}                            \\ \hline
